On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 arity1.tex
Update arity1.tex

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dotted] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

@@

There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}. However, if it makes three bonds once, such as in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic. Similarly to case 1. in the previous section, (a), (b) and (c)in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a first corner of $\hexagon_p^n$ and  (e) in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a second corner of $\hexagon_p^n$. (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
        \fill (1.5, -0.5) node [below] {(a)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (-0.5, 0.866) -- (-1.0, 0.0);
        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(b)};
      \end{tikzpicture}\\

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(c)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(d)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dotted] [red] (-1.5, 0.866) -- (-1.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(e)};
      \end{tikzpicture}\\

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
        \fill [blue] (3.5, 0.866) circle [radius = 0.1];
        \draw [blue] (0.5, 0.866) -- (1.5, 0.866);
        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
        \draw [blue] (2.5, 0.866) -- (3.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
        \fill [blue] (1.0, 1.732) circle [radius = 0.1];
        \draw [blue] (0.5, 0.866) -- (1.0, 1.732);
        \draw [blue] (1.5, 0.866) -- (1.0, 1.732);
        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
      \end{tikzpicture}

    \end{tabular}
    \caption{Being nondeterministic when reaching a corner of $\hexagon_p^n$}
    \label{fig:hexcorner}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (1.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [left] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.0, 1.732) -- (1.5, 0.866);
        \draw [dotted] [red] (1.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (1.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (1.0, 1.732) -- (0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (-0.5, 0.866) node [left] {$(0, 1)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dotted] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dotted] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(1, 1)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dotted] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (4.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (3.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw (2.5, 0.866) -- (3.5, 0.866);
        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dotted] [red] (3.5, 0.866) -- (4.0, 0.0);
        \fill (1.5, -0.5) node [below] {(a)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (4.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (3.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw (2.5, 0.866) -- (3.5, 0.866);
        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dotted] [red] (3.5, 0.866) -- (4.0, 0.0);
        \fill (1.5, -0.5) node [below] {(b)};
      \end{tikzpicture}\\

>>>>

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

@@

There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}. If there are beads having a free hand at (1,0) and (-1,0), there will be at least two possibilities in Fig.~\ref{fig:beadi-1} when a bead $i-1$ is fixed at (0,0). It is nondeterministic and beads $i-1, i, i+1$ needs to make three hydrogen bonds to prevent from it. That is, it is impossible to put beads having a free hand at (-1,0), (0,0) and (1,0). It is impossible to realize (b) and (e) in Fig.~\ref{fig:3bonds}. (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1). If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic. Similarly to case 1. in the previous section, (a) and (c) in Fig.~\ref{fig:3bonds} become nondeterministic finally when it reaches a first corner of $\hexagon_p^n$.

\begin{figure}
  \begin{center}
    \begin{tabular}{ccccc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
        \fill (1.5, -0.5) node [below] {(a)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (-1.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(b)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(c)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-2.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(d)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (-1.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (-1.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
        \draw [dashed] [red] (-1.5, 0.866) -- (-1.0, 0.0);
        \fill (-0.5, -0.5) node [below] {(e)};
      \end{tikzpicture}\\

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw [dashed] [red] (-1.0, 0.0) -- (0.0, 0.0);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
      \end{tikzpicture}

    \end{tabular}
    \caption{When a bead$i-1$ is fixed at (0,0)}
    \label{fig:beadi-1}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (1.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [left] {$(1, 1)$};
        \fill (1.0, 0.0) node [below] {$(1, 0)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.0, 1.732) -- (1.5, 0.866);
        \draw [dashed] [red] (1.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (-0.5, 0.866) node [left] {$(0, 1)$};
        \fill (1.0, 0.0) node [below] {$(1, 0)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(1, 1)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (1.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (4.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (3.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw (2.5, 0.866) -- (3.5, 0.866);
        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
        \fill (1.5, -0.5) node [below] {(a)};
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (2.0, 0.0) circle [radius = 0.1];
        \fill (3.0, 0.0) circle [radius = 0.1];
        \fill (4.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (1.5, 0.866) circle [radius = 0.1];
        \fill (2.5, 0.866) circle [radius = 0.1];
        \fill (3.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \fill (0.5, 0.866) node [above] {$(1, 1)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (1.5, 0.866);
        \draw (1.5, 0.866) -- (2.5, 0.866);
        \draw (2.5, 0.866) -- (3.5, 0.866);
        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
        \fill (1.5, -0.5) node [below] {(b)};
      \end{tikzpicture}\\
